---
title: "Help!"
format: html
---

### Setting things up

You'll often want to include a sample of your dataframe rather than the whole thing, particularly if it's very large.

Ctrl + F7 will open a new source columntibble::tribble(
                                                                                                                                        ~ID, ~Organisation, ~Age, ~LOS, ~Death,
                                                                                                                                       243L,      "Trust3",  58L,   2L,     0L,
                                                                                                                                       165L,      "Trust5",  24L,   2L,     0L,
                                                                                                                                       110L,     "Trust10",  42L,   5L,     0L,
                                                                                                                                       164L,      "Trust4",  36L,   2L,     0L,
                                                                                                                                       209L,      "Trust9",  74L,   3L,     0L,
                                                                                                                                       158L,      "Trust8",  50L,   2L,     0L,
                                                                                                                                        17L,      "Trust7",  72L,   4L,     0L,
                                                                                                                                        58L,      "Trust8",  95L,  14L,     0L,
                                                                                                                                        67L,      "Trust7",  44L,   2L,     0L,
                                                                                                                                        86L,      "Trust6",  13L,   2L,     0L,
                                                                                                                                         7L,      "Trust7",  25L,   4L,     0L,
                                                                                                                                       280L,     "Trust10",  69L,   8L,     0L,
                                                                                                                                       120L,     "Trust10",  20L,   3L,     0L,
                                                                                                                                       263L,      "Trust3",  73L,   9L,     0L,
                                                                                                                                         5L,      "Trust5",  70L,  11L,     0L,
                                                                                                                                       278L,      "Trust8",  55L,   2L,     0L,
                                                                                                                                        28L,      "Trust8",  58L,  10L,     0L,
                                                                                                                                       192L,      "Trust2",   7L,   1L,     0L,
                                                                                                                                        38L,      "Trust8",  83L,   7L,     0L,
                                                                                                                                       191L,      "Trust1",  58L,   3L,     0L
                                                                                                                                       )


```{r}
library(dplyr)
library(datapasta)

fresh_data <- NHSRdatasets::LOS_model |> dplyr::slice_sample(n = 20) # slice_sample(prop=0.2) will randomly select 20% of rows
```

### Editing the data

```{r}
fresh_data |> datapasta::dpasta()

```
You can edit the resulting tibble, then assign it to an object.

```{r}
fresh_edited_data<-tibble::tribble(
                         ~ID, ~Organisation, ~Age, ~LOS, ~Death,
                         55L,      "some_other_name",  81L,  13L,     0L,
                        217L,      "a_different_name",  14L,   2L,     0L,
                        118L,      "Trust8",  14L,   2L,     0L,
                        183L,      "Trust3",  69L,   9L,     0L,
                          3L,      "Trust3",  93L,  12L,     0L,
                         32L,      "Trust2",  82L,   2L,     0L,
                        212L,      "Trust2",  59L,   4L,     0L,
                         26L,      "Trust6",  49L,  10L,     0L,
                         25L,      "some_other_name",  83L,   7L,     0L,
                        242L,      "Trust2",  90L,   7L,     0L,
                        247L,      "a_different_name",  70L,   5L,     0L,
                        264L,      "Trust4",  79L,   5L,     0L,
                        296L,      "Trust6",  32L,   6L,     0L,
                        105L,      "some_other_name",  15L,   1L,     0L,
                         53L,      "Trust3",  14L,  18L,     1L,
                         66L,      "Trust6",   8L,   1L,     1L,
                         93L,      "Trust3",  55L,   5L,     1L,
                        158L,      "Trust8",  50L,   2L,     0L,
                        210L,     "Trust10",  56L,   7L,     0L,
                        249L,      "Trust9",  74L,   8L,     0L
                        )

#Some code you want to use the dataframe in
ggplot2::ggplot(data = fresh_edited_data, aes(x=Organisation, y = Age)) +geom_point()
```

If you want to get help you could copy & paste the whole of the above chunk.


## Alternative way to create a dataframe from your data if you don't like datapasta.
### dput()

The dput() function can also be used to produce the code to create your dataframe.
```{r}
fresh_edited_data |> dput()
```


```{r}
other_edited_data <- structure(list(ID = c(55L, 217L, 118L, 183L, 3L, 32L, 212L, 26L, 
25L, 242L, 247L, 264L, 296L, 105L, 53L, 66L, 93L, 158L, 210L, 
249L), Organisation = c("some_other_name", "a_different_name", 
"Trust8", "Trust3", "Trust3", "Trust2", "Trust2", "Trust6", "some_other_name", 
"Trust2", "a_different_name", "Trust4", "Trust6", "some_other_name", 
"Trust3", "Trust6", "Trust3", "Trust8", "Trust10", "Trust9"), 
    Age = c(81L, 14L, 14L, 69L, 93L, 82L, 59L, 49L, 83L, 90L, 
    70L, 79L, 32L, 15L, 14L, 8L, 55L, 50L, 56L, 74L), LOS = c(13L, 
    2L, 2L, 9L, 12L, 2L, 4L, 10L, 7L, 7L, 5L, 5L, 6L, 1L, 18L, 
    1L, 5L, 2L, 7L, 8L), Death = c(0L, 0L, 0L, 0L, 0L, 0L, 0L, 
    0L, 0L, 0L, 0L, 0L, 0L, 0L, 1L, 1L, 1L, 0L, 0L, 0L)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -20L))
```









### An alternative way to modify your data for sharing 

```{r}
#create a dataframe of organisation names and aliases
Organisation <- unique(NHSRdatasets::LOS_model$Organisation)
length(Organisation) #checks the length of the vector Organisation
alias <- letters[1:10] #if you want to automate this you could use letters[1:length(Organisation)]
df <- data.frame(Organisation, alias) #combines the 2 vectors into a dataframe

# join the dataframe we just created to the LOS_model dataframe, select the columns we want & take a sample 10 rows, before piping it into dput() to create the code we can share.
dplyr::left_join(NHSRdatasets::LOS_model, df) |> select(Age, alias, Death) |> slice_sample(n=10) |> dput()
```


